\paperTitle

### 2014-01-31 doc/icml2014/intro.tex
done

% 3. People have approached unsupervised learning with the MoM magic sauce, but the sauce is limited.
Recently, unsupervised learning techniques based on the spectral method of moments
have offered a refreshing and promising perspective on
this learning problem
\citep{mossel2005learning,
hsu09spectral,
bailly2010spectral,
song2011spectral,
anandkumar11tree,anandkumar12moments,anandkumar12lda,
hsu12identifiability,
balle12automata}.
%\todo{make sure we are citing the right people}
These methods exploit the linear algebraic properties of the model to
factorize the moments into parameters, providing strong theoretical guarantees.
However, they apply to a limited set of models, and are thus
not as broadly applicable as EM.

\begin{figure}[t]
  \label{fig:approach}
  \centering
  \subimport{figures/}{approach.tikz}
  \caption{
 % \todo{need three steps: tensor factorization, optimize composite likelihood, recover model parameters;}
  Overview of approach}
\end{figure}

@@

% 4. State what we do: exploit moment constraints to make the problem easier.
In this paper,
we show that a much broader class of directed and undirected graphical models can be consistently estimated,
specifically those in which each hidden variable has three conditionally
independent observed variables (``views'')---see \propertyref{bottleneck}.
The key idea is to leverage the spectral method of moments,
not to directly provide a consistent parameter estimate as in previous work,
but as partial constraints on a likelihood-based objective.
%For a broad class of directed and undirected graphical models

@@

%Our approach also applies to undirected log-linear latent variable
  %models, where we use the recovered marginals to make the learning
  %problem convex (\sectionref{undirected}).
Finally, our approach gracefully extends to more general model families
  in which we are unable to recover the marginal distributions for all
  hidden cliques; in such scenarios, we use posterior regularization to constrain
  EM.  
%\todo{Is this possible?:  We show that empirically, using such constraints alleviates local
%optima issues.}

>>>>

% 3. People have approached unsupervised learning with the MoM magic sauce, but the sauce is limited.
Recently, unsupervised learning techniques based on the spectral method of moments
have offered a refreshing perspective on
this learning problem
\citep{mossel2005learning,
hsu09spectral,
bailly2010spectral,
song2011spectral,
anandkumar11tree,anandkumar12moments,anandkumar12lda,
hsu12identifiability,
balle12automata}.
%\todo{make sure we are citing the right people}
These methods exploit the linear algebraic properties of the model to
factorize the moments into parameters, providing strong theoretical guarantees.
However, they apply to a limited set of models, and are thus
not as broadly applicable as EM.

\begin{figure}[t]
  \label{fig:approach}
  \centering
  \subimport{figures/}{approach.tikz}
  \caption{
 % \todo{need three steps: tensor factorization, optimize composite likelihood, recover model parameters;}
  Overview of our approach: we first use tensor factorization to learn the conditional moments for each hidden variable.
  Then we optimize a composite likelihood to recover the hidden clique marginals,
  given which we can extract the model parameters.
  }
\end{figure}

@@

% 4. State what we do: exploit moment constraints to make the problem easier.
In this paper,
we show that a much broader class of discrete directed and undirected graphical models can be consistently estimated,
specifically those in which each hidden variable has three conditionally
independent observed variables (``views'')---see \propertyref{bottleneck}.
The key idea is to leverage the spectral method of moments,
not to directly provide a consistent parameter estimate as in previous work,
but as partial constraints on a likelihood-based objective.
%For a broad class of directed and undirected graphical models

@@

%Our approach also applies to undirected log-linear latent variable
  %models, where we use the recovered marginals to make the learning
  %problem convex (\sectionref{undirected}).
%Finally, our approach gracefully extends to more general model families
%  in which we are unable to recover the marginal distributions for all
%  hidden cliques; in such scenarios, we use posterior regularization to constrain
%  EM.  
%\todo{Is this possible?:  We show that empirically, using such constraints alleviates local
%optima issues.}
